---
title: "Student How To Guide - BU Forecasting Challenge"
author: "Katherine Rein"
output: html_document
---


Welcome to the How To Guide for the BU Forecasting Challenge.
Here you will see a framework for the basic aspects of the challenge.
Each step will have an R and a Python code block -- which is which is labeled in {} brackets.

## Setting Up the Environment

```{r}
library(readr)
library(httr)
```

If you would like to use Python, then you have to have a Python environment set up.

1. Go to https://www.anaconda.com/download and scroll down to Miniconda Installers.
Download the correct installer for your computer. Complete the installation steps.

2. Download the following yaml file: https://uri.osn.mghpcc.org/bu4cast-ci/read/challenges/targets/project_id=bu4cast/dataclass_env.yaml

3. Open a Terminal (macOS) or Anaconda Prompt (Windows) window.

4. Run the following commands:

conda env create -f dataclass_env.yml
conda activate dataclass

Now you can run the following code blocks:

```{r}
# Activate Python Environment
library(reticulate)
use_condaenv("dataclass", required = TRUE)
```

This will create an error but don't worry you didn't do anything wrong.

```{python}
# Import modules
import pandas as pd
import requests
import tempfile
import numpy as np
from io import StringIO
```


## S3 Minio Buckets - Read

First things first, you need to understand how and where the raw data is stored.
All of the data for each challenge is stored in a targets file in a
place called an S3 Minio bucket. Minio is simply the kind of S3 bucket. S3 buckets
are a storage system similar to how you might store files in Google Drive. Just like
any other file storage system, there is a file path to the data. 

We will test reading to the S3 Bucket with the urban targets data, but I have
included the urls for all 3.

```{r}
base_url = 'https://uri.osn.mghpcc.org/bu4cast-ci/read/challenges/project_id=bu4cast/targets/'
urban_url = paste(base_url, 'urban-targets.csv', sep = "")
disease_url = paste(base_url, 'tropical-disease-targets.csv', sep = "")
coastal_url = paste(base_url, 'coastal-targets.csv', sep = "")

test_read_urban = read.csv(urban_url)
print(test_read_urban)
```

```{python}
base_url = 'https://uri.osn.mghpcc.org/bu4cast-ci/read/challenges/project_id=bu4cast/targets/'
urban_url = base_url + 'urban-targets.csv'
disease_url = base_url + 'tropical-disease-targets.csv'
coastal_url = base_url + 'coastal-targets.csv'
test_read_urban = pd.read_csv(urban_url)
print(test_read_urban)
```


## S3 Minio Buckets - Write

After you have the read working from the S3 Buckets, we now need to practice
writing to the S3 Bucket. We will practice this with a randomly generated csv file.
You will be writing to a challenge named test so that you can make sure it works
without actually submitting predictions. Make sure to change the variable team_name_example.

```{r}
# Randomly Generate Data
test_data = data.frame(
  id = 1:100,                        
  age = sample(18:80, 100, replace = TRUE),  
  height = rnorm(100, mean = 170, sd = 10),  
  weight = rnorm(100, mean = 70, sd = 15)
)

# Create a temp CSV file
test_file <- tempfile(fileext = ".csv")
write.csv(test_data, test_file, row.names = FALSE)

# Create filename
challenge_name_example = 'test'
team_name_example = 'KAIYA' ## FILL IN WITH YOUR OWN TEAM NAME EXAMPLE
url <- paste0("https://uri.osn.mghpcc.org/bu4cast-ci/write/challenges/project_id=bu4cast/forecasts/", challenge_name_example, "/",team_name_example, "-submission.csv")

# Write to bucket
res <- PUT(url, body = upload_file(test_file))

if (status_code(res) %in% c(200, 204)) {
  message("CSV upload succeeded!")
} else {
  message("Failed. Status: ", status_code(res))
}

```

```{python}
# Randomly Generate Data
test_data = pd.DataFrame({
    'id': range(1, 101),
    'age': np.random.randint(18, 81, 100),
    'height': np.random.normal(170, 10, 100),
    'weight': np.random.normal(70, 15, 100)
})

# Create a temp CSV file
with tempfile.NamedTemporaryFile(mode = 'w', suffix = '.csv', delete = False) as f:
    test_file = f.name
    test_data.to_csv(f.name, index = False)

# Create filename
challenge_name_example = 'test'
team_name_example = 'KAIYA' ## FILL IN WITH YOUR OWN TEAM NAME EXAMPLE
url = f"https://uri.osn.mghpcc.org/bu4cast-ci/write/challenges/project_id=bu4cast/forecasts/{challenge_name_example}/{team_name_example}-submission.csv"

# Write to bucket
with open(test_file, 'rb') as f:
    res = requests.put(url, data=f)

if res.status_code in [200, 204]:
    print("CSV upload succeeded!")
else:
    print(f"Failed. Status: {res.status_code}")
    print(res.text)
```



